### 2018-08-08 paper/sphinxes.tex
small edits

\subsection{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

@@

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
excellent description in the original Sphinx paper~\cite{Sphinx}.

@@

If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
If \(t\) is already in the table of seen packets, drop the packet.
Otherwise, add \(t\) to the table and decrypt \(\beta\):
\begin{equation*}
  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
    \kappa}\}
  \oplus \prg(\hash_\prg(s_i))
\end{equation*}

>>>>

\section{\Sphinxes: the Sphinx header format Extended for Sets of nodes}%
\label{Sphinxes}

@@

We will now give an overview of the Sphinx header format.
The idea is not to give a detailed description of Sphinx, but to give the 
reader enough understanding of Sphinx to understand the changes we make to 
achieve \Sphinxes.
For a more detailed understanding of Sphinx, we refer the reader to the 
description in the original Sphinx paper~\cite{Sphinx}.

@@

If the \ac{MAC} computed correctly, compute \(t\gets \hash_\tau(s_i)\).
If \(t\) is already in the table of seen (mix, not IP) packets, drop the packet.
Otherwise, add \(t\) to the table and decrypt \(\beta\):
\begin{equation*}
  L'\concat C'\concat \gamma'\concat \beta'\gets \{\beta\concat 0_{w_H 
    \kappa}\}
  \oplus \prg(\hash_\prg(s_i))
\end{equation*}
